Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-08-30 paper/ms.tex
MNRAS version

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field size by
constructing mock fields from a large cosmological N-body
simulation matching the geometries of observed fields. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm   min}<M_{\rm h}<M_{\rm max}$ can only host
one detectable LAE with a probability $f_{\rm occ}$. The main motivation to
build such a model is to avoid the large uncertainties in the estimation of
\ly luminosities. We find that the clustering and number density information are
insufficient to impose a tight constraint on the escape fraction. On
the other hand the minium mass and maximum mass are tightly
constrained to be $M_{\rm max}<10^{12}$\hMsun and
$10^{10}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$.  We also find
that all models have a narrow mass range $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than $1.0$ dex,
with the vast majority in the range $\Delta M<0.5$ dex. Already
published constraints on the mass range and occupation fraction are a sub-set of
the models we report in this \documentname. Our results present an
inconclusive response as to which is the occupation fraction for LAEs
at $z=3.1$. A precise answer requires robust physical models for the
connection between dark matter, star formation and the escape of \ly
radiation. That kind of modelling should also be able to provide a
plausible explanation for the narrow ange in mass $\Delta M<1.0$ dex
derived here for the halos hosting LAEs at $z=3.1$.

@@

Most models of galaxy formation find that halo mass can be
used to predict galaxy properties such as the stellar mass and
star formation rate \citep{Behroozi2012}. Processes that regulate the
star formation cycle are also though to be strongly dependent on its
halo mass.  For these reasons, finding the typical dark matter halo mass
hosting LAEs represents a significant step forward to understand the
nature of this galaxy population in the context of Lambda Cold Dark
Matter ($\Lambda$CDM) paradigm.

@@

In addition to the uncertainties in the astrophysical processes
describing star formation in galactic populations,the calculation
of the fraction of \ly photons that escape the galaxy to the observer
is another debated step. Given the resonant nature of the \ly line,
the radiative transfer of \ly is sensitive to the density,
temperature, topology and kinematics of the neutral Hydrogen in the
interstellar medium
(ISM). This problem can be tackled with Monte Carlo simulations for the
radiative transfer, however the complexity of the relevant physical
processes makes it difficult to achieve a robust consensus on what is
the theoretical expected value for the \ly escape fraction
at high redshift
\citep{Neufeld1991,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\linewidth,angle=0]{./plots/Figure0.pdf}
\caption{ \label{fig:distros} Spatial distribution of a LAEs mock
  survey for a model with parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt{match}}
  method. The larger panel shows $7$ mock
  fields together mimicking the SSA22 region. The intermediate panel
  shows $3$ mock fields corresponding to the SXDS region. The lower
  panels represent the SDF and GOODS-North fields. The same model has
  another 14 associated mock surveys build from different regions in
  the simulation, but constructed following the same pattern in the
  {\texttt{match}} method.}
\end{center} 
\end{figure*}

We assume that a dark matter halo can only host one
detectable LAE at most.  There are three parameters that
decide whether a halo host a LAE: the lower and upper bounds for the
mass range, $M_{\rm min}< M_{\rm h} < M_{\rm max}$, where LAEs reside and the fraction $f_{\rm occ}$ of such halos that host a detectable LAE. The reader
must keep in mind that the physical interpretation of the occupation
fraction $f_{\rm occ}$ convolves two phenomena: the actual presence of a star
forming galaxy in a halo and its detectability as a LAE.  We do not
peform a explicit modeling for LAE detectability. Our model does not
assign a luminosity or escape fraction to each LAE.  We are only
interested in constraining the halo mass range hosting detectable LAEs
under the conditions defined by \cite{Yamada2012}.

@@

Figure \ref{fig:distros} shows the spatial distribution for one mock
survey constructed using the {\texttt{match}} method. Each field
corresponds to one of the observational fields. The model parameters
to build it are $M_{\rm min}=10^{10.4}$\hMsun, $M_{\rm
  max}=10^{0.5}$\hMsun and $f_{\rm occ}=0.1$. It is only one out of
the $15$ different mock surveys that are constructed for each
model. We note that we use $15\times 12=180$ mock fields out of the
total of $210$ available sub-volumes. The reason is that the {\texttt{match}}
method imposes constraints on the way the $7$ fields mimicking the
SSA22 can be distributed. This restriction makes unusuable some of the
sub-volumes in the box. We decide to keep the number of mock surveys
fixed to $15$ also for the {\texttt{random}} method in order to allow a
fair comparison between the two methods.

@@

The observed and mock ACF are fit to a power-law function:
\begin{equation}
\omega(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{-\beta}, 
\label{eq:fitting}
\end{equation}
where $\theta_0$ and $\beta$ are free parametres. The fit is donde
using a least square minimization procedure. For each mock field we obtain a
covariance matrix that gives us the uncertainty in the parameters $\beta$ and
$\theta_0$. Using the $15$ mock fields in a mock survey, we compute a
mean value for the parameters and its associated uncertainty as the
cuadratic average of the uncertainties in the fitting procedure. We
consider that a model is consistent with observations if the two
parameters $\beta$ and $\theta_0$ are equal within a $1$-$\sigma$
range.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.10\linewidth,angle=0]{./plots/Fig1.pdf}
\caption{ \label{fig:halos} Surface density of dark
  matter halos as a function of a minimum halo mass to count the
  total number of elements in a volume. Each line represents one of the
  $210$ volumes of dimensions $46\times 35\times 41$ h${-3}$Mpc$^{3}$
  in the Bolshoi simulation. The horizontal gray band represents the
  range of surface densities observed for LAEs at $z=3.1$ as reported
  by \citep{Yamada2012}.}
\end{center} 
\end{figure}

@@

Figure \ref{fig:halos} also illustrates the impact of cosmic
variance. At fixed mass there is an scatter of $0.3-0.6$ dex in the
number density abudance.  A consequence of this variation is that
models with the same mass range and occupation fraction can have mock
fields with number densities varying up to a factor of $\sim
2-5$. This scatter is comparable to the $0.3$ dex scatter coming from 
observations. In the same Figure \ref{fig:halos} we see that at fixed
number density, around the range allowed by observations, there is an
scatter in the masses of $0.4-0.5$ dex.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}
\vspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}
%\hspace{5mm}
%\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm    min}-f_{\rm
    occ}$ (right) planes for all models with  KS test values
  $P>0.05$. The color code corresponds to the number of  mock surveys
  compatible with observations. Only regions of parameter  space with
  at least one consistent mock survey are  included. \label{fig:landscape}}     
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.95\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
%\hspace{5mm}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
\end{center} 
\caption{ Number of models with at least $N_{\rm high-P}$ mock surveys
  consistent with the observed surface number density
  distribution in terms of the KS-test values $P>0.05$. Only $\sim
  100$ models have all their mocks consistent with observations. 
  \label{fig:high_success_rate}.}  
\end{figure}

@@

We conclude that conditions on the number density statistics, even if they are
very strict, only put strong constraints on the minimum mass $M_{\rm
  min}$ but not on the other two parameter of the model $M_{\rm max}$
and $f_{\rm occ}$. In the next section we use additional observational
information to constrain these paremeters.

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock.pdf} 
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_f_occ_mock.pdf}
\end{center}  
\caption{Favored regions in parameter space when the constraints on
  the maximal number of consistent mocks is imposed. Only the results
  for the {\texttt match} method are shown.
  \label{fig:restriction_mock}}  
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation_maxden.pdf} 
\hspace{5mm}  
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation_meanden.pdf} 
\end{center}
\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\beta$) 
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green cross to observations by \citet{Hayashino2004} and
\citet{Ouchi2010}. The error bars in the   theoretical data correspond
to the standard deviation from the different mocks surveys. 
\label{fig:correlation_parameters}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_meanden_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_meanden_f_occ.pdf}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_maxden_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_maxden_f_occ.pdf}
\end{center}
\caption{Planes $M_{\rm min}$ vs $M_{\rm max}$ (left), $M_{\rm min}$
  vs $f_{\rm occ}$ (right). The squares represent the models when both
   constraints on the maximal number of consistent mocks and the
  angular correlation function are included. Upper panels correspond
  checks the consistency against the observational data of
  \citet{Ouchi2010}, while lower panels show results for \citet{Hayashino2004}
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

Figure \ref{fig:correlation_parameters} shows the main results in a
$\theta_{0}-\beta$  plane where the average and standard deviation
over the mocks is shown in comparison with the result derived from
observations. In the left panel Figure \ref{fig:correlation_parameters} we see
how the observational ACF measured by \cite{Hayashino2004} 
can be successful in reducing the total number of possible models. The
right panel shows the results for fields in the mock catalog with an
average number density compared against the fit of the data
reported by \cite{Ouchi2010}. In this case we find that there are
large uncertainties coming from the observational data, and only a reduced
fraction of the modesl can be discartded.

@@

In the Results Section we start by matching the rough numbers for the
galaxy surface number density. This sets the median mass of all
successful models to the broad range $(10^{10}-10^{12})$ \hMsun for
$M_{\rm min}$ and $M_{\rm max}$. We include additional criteria on the
number of mock surveys that must be consistent observations
and the information from the angular correlation function, reducing
the number of feasible models. We end up with $\sim 25$ models out of
the initial $9000$ possible combination of parameters.

In order to make a physical interpretation of these models we use 
the halo mass range, defined as $\Delta M=\log_{10}M_{\rm max} -
\log_{10}M_{\rm  min}$, together with the occupation fraction $f_{\rm
  occ}$ to classify all the successful models into two families:

\begin{itemize}
\item[(1)] Low $f_{\rm occ}\leq 0.3$, $M_{\rm min}\leq 10^{10.8}\hMsun$ and low $\Delta M\leq 1.0$
  dex: 12 models. 
\item[(2)] High $f_{\rm occ}> 0.3$, $M_{\rm min}\geq 10^{10.8}\hMsun$ and
  low $\Delta M\leq 1.0$: 11 models 
\end{itemize}

The full list of paramenter in the two families is summarized in Table
\ref{table:firstfamily} and Table \ref{table:secondfamily}. We do not
have a clear majority of any family. This leads us to the following
two conclusions. First, the occupation fraction cannot be constrained
based on clustering anaylsis. Second, the halos hosting LAEs have a
narrow mass range.

The existence of a narrow mass rango for halo masses has different
possible explanations. A cut at the low mass end $M_{\rm min}$ can be
interpreted in terms of the minimal halo star formation rate needed to
produce the minimal \ly  luminosity to be above a given detection
threshold.  However, under the reasonable assumption of star formation
rate increasing with halo mass, the cut at higher halo masses requires
a different justification. There are two complementary physical
scenarios that can provide it.

One scenario can be presented in terms of a decreasing escape fraction
of \ly radiation in massive systems. There are detailed models for
radiative transfer that support the idea that massive galaxies with
higher metallicities have larger dust contents and less concentrated
ISM than lower mass systems. Due to the resonant nature of the \ly
line the probability of absorption  of \ly photons increases in
massive systems, producing high absorption of \ly photons but not of
continuum or other non-resonant lines \citep{Laursen2009,ForeroRomero2011}.

A second scenario is that larger systems have more extended gaseous
envelopes which due to resonance effects of the \ly line, can induce a
low surface brightness and a broader line, making these systems less
observable in narrow band filter surveys
\citep{Laursen2009,Zheng2010}.

The preference for narrow $\Delta M$ ranges to host LAEs 
and the small presence of reasonable models with $M_{\rm max}>
10^{12}$\hMsun also follows theoretical and observational
insights for high-z galaxies where the most massive systems are not
bright \ly sources \citep{ForeroRomero2012,Shapley2003}.

@@

Theoretical intepretations of blind galaxy surveys at $z=2.2$ find a
volume weighted escape fraction $f_{\rm esc}\sim 0.1-0.2$
\cite{Hayes2010}, similar results are obtained in a recent theoretical
study of observational data in a wide redshift range $0<z<6$
\citep{Dijkstra2013}.

\cite{Hayes2010} showed that the luminosity function for
LAEs at $z=2.2$ is consistent with the escape fraction being constant
for every galaxy regardless of its luminosity. From this results they
derive that almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$. \cite{Dijkstra2013} uses similar
methods to find an average \ly escape fraction in high-z galaxies,
they conclude that there is a range in luminosity where the escape
fraction they derive at $z\sim 3.0$, $f_{\rm esc}=(17\pm 5)\%$, could
be interpreted as an occupation fraction $f_{\rm occ}\sim 0.2$.

We consider a success that our model indeed includes such low
occupation fraction models. The observational evidence from galaxy
surveys seem to disfavor the second family of models with high
occupation fractions. Nevertheless, it remains a task for galaxy
formation models to explain the mass range $\Delta M<0.5$ in the models.

@@

Observational based on the ACF inferred from photometric measurements
in the Extended Chandra Deep Field South have shown that the median
dark matter masses of h los hosting LAEs is $\log_{10}M_{\rm
  med}=10.9^{+0.5}_{-0.9}$\Msun, with a corresponding occupation
fraction of $1-10\%$  \citep{Gawiser07}.  Our results are in a general
good agreement with those estimates for the host mass. This is not
completely unexpected given that we have also required consistency
with ACF measurements.

The novelty in our approach is that we have a detailed estimate for 
host halo mass range together with the escape fraction. This allows us
to demonstrate that the halo mass range could be very narrow $\Delta M <
0.2$dex, something that cannot be inferred from ACF analysis alone.

We also find that an ACF analysis on a single data-set is not enough to rule
out models with a high occupation fraction $f_{\rm occ}>0.3$, which
represent half of our best models. These models cannot be
considered unfavorable based on a clustering analysis only, it
requires additional information from galaxy surveys, as we have
presented in the previous section.

\cite{Ouchi2010} presents an analysis of LAE observations in the
redshift interval $3.1<z<7.0$. At $z=3.1$ They quote an average
mass for the host dark matter halos of $M_{h}=2.9^{+24.0}_{-2.9}\times
10^{10}$ \hMsun with a corresponding duty cycle of $0.008\pm
0.03$.  This broadly matches the expectations from the first family of
models, also summarized in Table \ref{table:firstfamily}. In
particular it seems to favor only the very low occupations
fractions.

We conclude this section by noting that the uncertainties on
the preferred masses in \citep{Gawiser07} and \cite{Ouchi2010} are
found with in the intervals $M_{\rm min}$ and $M_{\rm max}$ of our
models.

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
10.1 &10.2 & 0.1 & 0.1\\
10.3 &10.5 & 0.1 & 0.2\\
10.4 &10.7 & 0.1 & 0.3\\
10.5 &10.6 & 0.3 & 0.1\\
10.5 &10.9 & 0.1 & 0.4\\
10.5 &11.0 & 0.1 & 0.5\\
10.6 &11.2 & 0.1 & 0.6\\
10.6 &11.4 & 0.1 & 0.8\\
10.6 &11.7 & 0.1 & 1.1\\
10.7 &11.0 & 0.2 & 0.3\\
10.8 &11.2 & 0.2 & 0.4\\
10.8 &11.3 & 0.2 & 0.5\\\hline
\end{tabular}
\end{center}
\caption{\label{table:firstfamily}List of parameters for the first
  family of models. Narrow mass range $\Delta M\leq 1.0$dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}

>>>>

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field size by
constructing mock fields from a large cosmological N-body
simulation matching the geometries of observed fields. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm   min}<M_{\rm h}<M_{\rm max}$ can only host
one detectable LAE with a probability $f_{\rm occ}$. The main motivation to
build such a model is to avoid the large uncertainties in the estimation of
\ly luminosities. We find that the clustering and number density information are
insufficient to impose a tight constraint on the escape fraction. On
the other hand the minimum mass and maximum mass are tightly
constrained to be $M_{\rm max}<10^{12}$\hMsun and
$10^{10}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$.  We also find
that all models have a narrow mass range $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than $1.0$ dex,
with the vast majority in the range $\Delta M<0.5$ dex. Already
published constraints on the mass range and occupation fraction are a sub-set of
the models we report in this \documentname. Our results present an
inconclusive response as to which is the occupation fraction for LAEs
at $z=3.1$. A precise answer requires robust physical models for the
connection between dark matter, star formation and the escape of \ly
radiation. That kind of modelling should also be able to provide a
plausible explanation for the narrow range in mass $\Delta M<1.0$ dex
derived here for the halos hosting LAEs at $z=3.1$.

@@

Most models of galaxy formation find that halo mass can be
used to predict galaxy properties such as the stellar mass and
star formation rate \citep{Behroozi2013a}. Processes that regulate the
star formation cycle are also though to be strongly dependent on its
halo mass.  For these reasons, finding the typical dark matter halo mass
hosting LAEs represents a significant step forward to understand the
nature of this galaxy population in the context of Lambda Cold Dark
Matter ($\Lambda$CDM) paradigm.

@@

In addition to the uncertainties in the astrophysical processes
describing star formation in galactic populations,the calculation
of the fraction of \ly photons that escape the galaxy to the observer
is another debated step. Given the resonant nature of the \ly line,
the radiative transfer of \ly is sensitive to the density,
temperature, topology and kinematics of the neutral Hydrogen in the
interstellar medium
(ISM). This problem can be tackled with Monte Carlo simulations for the
radiative transfer, however the complexity of the relevant physical
processes makes it difficult to achieve a robust consensus on what is
the theoretical expected value for the \ly escape fraction
at high redshift
\citep{Neufeld1991,Verhamme2006,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\linewidth,angle=0]{Figure0.pdf}
\caption{ \label{fig:distros} Spatial distribution of a LAEs mock
  survey for a model with parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt{match}}
  method. The larger panel shows $7$ mock
  fields together mimicking the SSA22 region. The intermediate panel
  shows $3$ mock fields corresponding to the SXDS region. The lower
  panels represent the SDF and GOODS-North fields. The same model has
  another 14 associated mock surveys build from different regions in
  the simulation, but constructed following the same pattern in the
  {\texttt{match}} method.}
\end{center} 
\end{figure*}

We assume that a dark matter halo can only host one
detectable LAE at most.  There are three parameters that
decide whether a halo host a LAE: the lower and upper bounds for the
mass range, $M_{\rm min}< M_{\rm h} < M_{\rm max}$, where LAEs reside and the fraction $f_{\rm occ}$ of such halos that host a detectable LAE. The reader
must keep in mind that the physical interpretation of the occupation
fraction $f_{\rm occ}$ convolves two phenomena: the actual presence of a star
forming galaxy in a halo and its detectability as a LAE.  We do not
perform a explicit modeling for LAE detectability. Our model does not
assign a luminosity or escape fraction to each LAE.  We are only
interested in constraining the halo mass range hosting detectable LAEs
under the conditions defined by \cite{Yamada2012}.

@@

Figure \ref{fig:distros} shows the spatial distribution for one mock
survey constructed using the {\texttt{match}} method. Each field
corresponds to one of the observational fields. The model parameters
to build it are $M_{\rm min}=10^{10.4}$\hMsun, $M_{\rm
  max}=10^{0.5}$\hMsun and $f_{\rm occ}=0.1$. It is only one out of
the $15$ different mock surveys that are constructed for each
model. We note that we use $15\times 12=180$ mock fields out of the
total of $210$ available sub-volumes. The reason is that the {\texttt{match}}
method imposes constraints on the way the $7$ fields mimicking the
SSA22 can be distributed. This restriction makes unable some of the
sub-volumes in the box. We decide to keep the number of mock surveys
fixed to $15$ also for the {\texttt{random}} method in order to allow a
fair comparison between the two methods.

@@

The observed and mock ACF are fit to a power-law function:
\begin{equation}
\omega(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{-\beta}, 
\label{eq:fitting}
\end{equation}
where $\theta_0$ and $\beta$ are free parameters. The fit is done
using a least square minimization procedure. For each mock field we obtain a
covariance matrix that gives us the uncertainty in the parameters $\beta$ and
$\theta_0$. Using the $15$ mock fields in a mock survey, we compute a
mean value for the parameters and its associated uncertainty as the
quadratic average of the uncertainties in the fitting procedure. We
consider that a model is consistent with observations if the two
parameters $\beta$ and $\theta_0$ are equal within a $1$-$\sigma$
range.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.10\linewidth,angle=0]{Fig1.pdf}
\caption{ \label{fig:halos} Surface density of dark
  matter halos as a function of a minimum halo mass to count the
  total number of elements in a volume. Each line represents one of the
  $210$ volumes of dimensions $46\times 35\times 41$ $h^{-3}$ Mpc$^{3}$
  in the Bolshoi simulation. The horizontal gray band represents the
  range of surface densities observed for LAEs at $z=3.1$ as reported
  by \citep{Yamada2012}.}
\end{center} 
\end{figure}

@@

Figure \ref{fig:halos} also illustrates the impact of cosmic
variance. At fixed mass there is an scatter of $0.3-0.6$ dex in the
number density abundance.  A consequence of this variation is that
models with the same mass range and occupation fraction can have mock
fields with number densities varying up to a factor of $\sim
2-5$. This scatter is comparable to the $0.3$ dex scatter coming from 
observations. In the same Figure \ref{fig:halos} we see that at fixed
number density, around the range allowed by observations, there is an
scatter in the masses of $0.4-0.5$ dex.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig2_match_P5.pdf}
\vspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{Fig3_match_P5.pdf}
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm    min}$-$f_{\rm
    occ}$ (right) planes for all models with  KS test values
  $P>0.05$. The color code corresponds to the number of mock surveys
  compatible with observations. Only regions of parameter  space with
  at least one consistent mock survey are  included. \label{fig:landscape}}     
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.95\linewidth,angle=0]{Fig4_match_P5.pdf}
\end{center} 
\caption{ Number of models with at least $N_{\rm high-P}$ mock surveys
  consistent with the observed surface number density
  distribution in terms of the KS-test values $P>0.05$. Only $\sim
  100$ models have all their mocks consistent with observations. 
  \label{fig:high_success_rate}.}  
\end{figure}

@@

We conclude that conditions on the number density statistics, even if they are
very strict, only put strong constraints on the minimum mass $M_{\rm
  min}$ but not on the other two parameter of the model $M_{\rm max}$
and $f_{\rm occ}$. In the next section we use additional observational
information to constrain these parameters.

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig5_match_mass_mock.pdf} 
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{Fig5_match_f_occ_mock.pdf}
\end{center}  
\caption{Favored regions in parameter space when the constraints on
  the maximal number of consistent mocks is imposed. Only the results
  for the {\texttt{match}} method are shown.
  \label{fig:restriction_mock}}  
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{power_law_correlation_maxden.pdf} 
\hspace{5mm}  
\includegraphics[width=0.46\linewidth,angle=0]{power_law_correlation_meanden.pdf} 
\end{center}
\caption{Values for the free parameters $\theta_{0}$ and $\beta$
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green cross to observations by \citet{Hayashino2004} (left) and
\citet{Ouchi2010} (right). The error bars in the theoretical data correspond
to the quadratic average of the fitting errors for each mock survey
\label{fig:correlation_parameters}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_meanden_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_meanden_f_occ.pdf}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_maxden_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_maxden_f_occ.pdf}
\end{center}
\caption{Planes $M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
    min}$-$f_{\rm occ}$ (right). with the models fulfilling both
   constraints on the maximal number of consistent mocks and the
  angular correlation function. Upper panels correspond
  checks the consistency with the observational data of
  \citet{Ouchi2010}. Lower panels show results after comparison
  against \citet{Hayashino2004}
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

Figure \ref{fig:correlation_parameters} shows the main results in a
$\theta_{0}-\beta$  plane where the average and standard deviation
over the mocks is shown in comparison with the result derived from
observations. In the left panel Figure \ref{fig:correlation_parameters} we see
how the observational ACF measured by \cite{Hayashino2004} 
can be successful in reducing the total number of possible models. The
right panel shows the results for fields in the mock catalog with an
average number density compared against the fit of the data
reported by \cite{Ouchi2010}. In this case we find that there are
large uncertainties coming from the observational data, and only a reduced
fraction of the models can be discarded.

@@

In the previous Section we started by matching the rough numbers for the
galaxy surface number density. This sets the median mass of all
successful models to the broad range $(10^{10}$-$10^{12})$ \hMsun for
$M_{\rm min}$ and $M_{\rm max}$. Then we included additional criteria on the
number of mock surveys that must be consistent observations
and the information from the angular correlation function, reducing
the number of feasible models. We ended up with $23$ models out of
the initial $9000$ possible combination of parameters.

Now we define the halo mass range $\Delta M=\log_{10}M_{\rm max} -
\log_{10}M_{\rm  min}$, to use it together with the occupation
fraction, $f_{\rm occ}$, and the minimum mass $M_{\rm min}$ to
classify all the successful models into two families:

\begin{itemize}
\item[(1)] Low $f_{\rm occ}\leq 0.3$, $M_{\rm min}\leq 10^{10.8}\hMsun$ and low $\Delta M\leq 1.0$
  dex: 12 models. 
\item[(2)] High $f_{\rm occ}> 0.3$, $M_{\rm min}\geq 10^{10.8}\hMsun$ and
  low $\Delta M\leq 1.0$: 11 models 
\end{itemize}
%
The full list of parameter in the two families is summarized in Table
\ref{table:firstfamily} and Table \ref{table:secondfamily}. We do not
have a clear majority of any family. This leads us to the following
two conclusions. First, the occupation fraction cannot be constrained
based on clustering analysis. Second, the halos hosting LAEs have a
narrow mass range.

The existence of a narrow mass range for halo masses has different
possible explanations. A cut at the low mass end, $M_{\rm min}$, can be
interpreted in terms of the minimal halo star formation rate needed to
produce the \ly luminosity needed to be above a given detection
threshold.  However, under the reasonable assumption of star formation
rate increasing with halo mass, the cut at higher halo masses $M_{\rm
  max}$requires a different justification. There are two complementary physical
scenarios that could provide it.

One scenario can be presented in terms of a decreasing escape fraction
of \ly radiation in massive systems. Detailed galaxy formation models
support the idea that massive galaxies with higher metallicities have
larger dust contents and less concentrated ISM than lower mass
systems. Due to the resonant nature of the \ly line the probability of
absorption  of \ly photons increases in massive systems, producing
high absorption of the \ly line but not of UV continuum or other
non-resonant lines \citep{Laursen2009,ForeroRomero2011}. In a second
scenario larger systems have more extended gaseous envelopes which due
to resonance effects of the \ly line, induces a low surface brightness
and a broader line, making these systems less observable in narrow
band filter surveys \citep{Laursen2009,Zheng2010}.

@@

Theoretical interpretations of blind galaxy surveys at $z=2.2$ find a
volume weighted escape fraction $f_{\rm esc}\sim 0.1-0.2$
\cite{Hayes2010}, similar results are obtained in a recent theoretical
study of observational data in a wide redshift range $0<z<6$
\citep{Dijkstra2013}.

\cite{Hayes2010} showed that the luminosity function for
LAEs at $z=2.2$ is consistent with the escape fraction being constant
for every galaxy regardless of its luminosity. From this results they
derive that almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$. \cite{Dijkstra2013} use similar
methods to find an average \ly escape fraction in high-z galaxies,
they conclude that there is a range in \ly luminosity where the escape
fraction they derive at $z\sim 3.0$, $f_{\rm esc}=(17\pm 5)\%$, could
be interpreted as an occupation fraction $f_{\rm occ}\sim 0.2$. We
consider a success that our model indeed includes such low occupation
fraction models. The observational evidence from galaxy surveys seem
to disfavor the second family of models with high occupation
fractions. Nevertheless, it remains an open task to explain the narrow
mass range $\Delta M<0.5$ in most of the models.

@@

Observational evidence based on the ACF inferred from photometric
measurements in the Extended Chandra Deep Field South has shown that
the median dark matter masses of h los hosting LAEs is
$\log_{10}M_{\rm  med}=10.9^{+0.5}_{-0.9}$\Msun, with a corresponding
occupation fraction of $1-10\%$  \citep{Gawiser07}.  \cite{Ouchi2010}
presents analysis of LAE observations in the redshift interval
$3.1<z<7.0$ and at $z=3.1$ They quote an average mass for the host
dark matter halos of $M_{h}=2.9^{+24.0}_{-2.9}\times 10^{10}$ \hMsun
with a corresponding duty cycle of $0.008\pm 0.03$.

Our results are in a general good agreement with those estimates for
the host mass. This is not completely unexpected given that we have
also required consistency with ACF measurements. These expectations
are matched by the first family of models, also summarized in Table
\ref{table:firstfamily}. These models, which favor only the very
low occupations fractions, are also consistent in that regards with
the observational expectations.

The novelty in our results is that we have a detailed estimate for 
host halo mass range together with the escape fraction. This allows us
to demonstrate that the halo mass range can in some cases be narrow $\Delta M <
0.3$dex, something that cannot be inferred from ACF analysis alone.
Furthermore, In contrast to \citep{Gawiser07} and \citep{Ouchi2010} we
find that an ACF analysis on a single data-set is not enough to rule
out models with a high occupation fraction $f_{\rm occ}>0.3$, which
represent half of our best models.

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
10.1 &10.2 & 0.1 & 0.1\\
10.3 &10.5 & 0.1 & 0.2\\
10.4 &10.7 & 0.1 & 0.3\\
10.5 &10.6 & 0.3 & 0.1\\
10.5 &10.9 & 0.1 & 0.4\\
10.5 &11.0 & 0.1 & 0.5\\
10.6 &11.2 & 0.1 & 0.6\\
10.6 &11.4 & 0.1 & 0.8\\
10.6 &11.7 & 0.1 & 1.1\\
10.7 &11.0 & 0.2 & 0.3\\
10.8 &11.2 & 0.2 & 0.4\\
10.8 &11.3 & 0.2 & 0.5\\\hline
\end{tabular}
\end{center}
\caption{\label{table:firstfamily}List of parameters for the first
  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}
